ML comparison

### 2020-10-10 src/s_ml.Rmd
first runs done of ml comparison

f_run_all <- function(methods, list_of_caret_grids, f_data_generator){
  x <- f_data_generator()
  r_stars <- vector(length = length(methods))
  for(i in seq_along(r_stars))
    r_stars[i] <- max(f_replicate_gridded(x, methods[i], list_of_caret_grids[[i]]))
  return(tibble(r_star=r_stars, method=methods))
}

@@

tunegrid_gbm <- expand.grid(interaction.depth=3, 
                             n.trees = 50,
                             shrinkage=0.1,
                             n.minobsinnode=10)
tunegrid_rf <- tibble(mtry = 1:2)
tunegrid_knn <- tibble(k = c(5, 10, 15, 20, 40))
tunegrid_svm <- tibble(C = c(0.25, 0.5, 0.75))
tunegrid_multinom <- tibble(decay=c(0.1, 0.2, 0.5, 1))
```

@@

temp_df <- f_run_all_replicates(2, c("gbm", "rf", "knn", "svmLinear", "multinom"),
          list(tunegrid_gbm, tunegrid_rf, tunegrid_knn, tunegrid_svm, tunegrid_multinom),
          f_data_ar1)
```

@@

temp_df <- f_run_all_replicates(2, c("gbm", "rf", "knn", "svmLinear", "multinom"),
          list(tunegrid_gbm, tunegrid_rf, tunegrid_knn, tunegrid_svm, tunegrid_multinom),
          f_data_8_schools)
```

@@

temp_df <- f_run_all_replicates(2, c("gbm", "rf", "knn", "svmLinear", "multinom"),
          list(tunegrid_gbm, tunegrid_rf, tunegrid_knn, tunegrid_svm, tunegrid_multinom),
          f_data_cauchy)
```

# Multivariate normal
```{r}

```

>>>>

f_run_all <- function(methods, list_of_caret_grids, f_data_generator){
  x <- f_data_generator()
  r_stars <- vector(length = length(methods))
  for(i in seq_along(r_stars)){
    print(methods[i])
    r_stars[i] <- max(f_replicate_gridded(x, methods[i], list_of_caret_grids[[i]]))
  }
  return(tibble(r_star=r_stars, method=methods))
}

@@

tunegrid_gbm <- expand.grid(interaction.depth=3, 
                             n.trees = 50,
                             shrinkage=0.1,
                             n.minobsinnode=10)
tunegrid_rf <- tibble(mtry = 1:2)
tunegrid_knn <- tibble(k = c(5, 10, 15, 20, 40))
tunegrid_svm <- tibble(C = c(0.25, 0.5, 0.75))
tunegrid_multinom <- tibble(decay=c(0.1, 0.2, 0.5, 1))
tunegrid_xgbtree <- expand_grid(nrounds = c(1, 10),
                       max_depth = c(1, 4),
                       eta = c(.1, .4),
                       gamma = 0,
                       colsample_bytree = .7,
                       min_child_weight = 1,
                       subsample = c(.8, 1))
```

@@

temp_df <- f_run_all_replicates(2, c("gbm", "rf", "knn", "svmLinear", "multinom"),
          list(tunegrid_gbm, tunegrid_rf, tunegrid_knn, tunegrid_svm, tunegrid_multinom),
          f_data_ar1)
temp_df <- readRDS("../data/ml_comp_ar1.rds")
temp_df %>%
  ggplot(aes(x=as.factor(method), y=r_star)) +
  geom_boxplot()
```

@@

temp_df <- f_run_all_replicates(2, c("gbm", "rf", "knn", "svmLinear", "multinom"),
          list(tunegrid_gbm, tunegrid_rf, tunegrid_knn, tunegrid_svm, tunegrid_multinom),
          f_data_8_schools)

temp_df <- readRDS("../data/ml_comp_8_schools.rds")
temp_df %>%
  ggplot(aes(x=as.factor(method), y=r_star)) +
  geom_boxplot()
```

@@

temp_df <- f_run_all_replicates(2, c("gbm", "rf", "knn", "svmLinear", "multinom"),
          list(tunegrid_gbm, tunegrid_rf, tunegrid_knn, tunegrid_svm, tunegrid_multinom),
          f_data_cauchy)
temp_df <- readRDS("../data/ml_comp_cauchy.rds")
temp_df %>%
  ggplot(aes(x=as.factor(method), y=r_star)) +
  geom_boxplot()
```

# Multivariate normal
```{r}
f_data_normal <- function(){
  N <- 250
  A <- rWishart(1, 250, diag(N))[,,1]
  model <- stan_model("mvt_250_ncp.stan")
  fit <- sampling(model, data=list(N=N, A=A), iter=1000, chains=4)
  x <- rstan::extract(fit, permuted=F)
  return(x)
}

temp_df <- f_run_all_replicates(20, c("xgbTree", "rf", "gbm"),
          list(tunegrid_xgbtree, tunegrid_rf, tunegrid_gbm),
          f_data_normal)
```
